### 2015-05-14 paper/paper.tex
new figures, after viva

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/sanaz.jpg}}]
{Sanaz Mostaghim}
is a professor of computer science at the Otto von Guericke University Magdeburg, Germany. Her current research interests are in the field of evolutionary computation, particularly in the areas of evolutionary multi-objective optimization, swarm intelligence and their applications in science and industry. She is an active IEEE member and is serving as an associate editor for IEEE Transactions on Evolutionary Computation and IEEE Transactions on Cybernetics.
\end{IEEEbiography}

>>>>

\begin{IEEEkeywords}
Monte Carlo Tree Search, Multi-Objective Optimization, Real-Time Games.
\end{IEEEkeywords}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{photos/sanaz.jpg}}]
{Sanaz Mostaghim} is a full professor of computer science at the Otto von Guericke University Magdeburg, Germany. She holds a PhD degree (2004) in electrical engineering and computer science from the University of Paderborn, Germany. She worked as a postdoctoral fellow at ETH Zurich in Switzerland and as a lecturer at Karlsruhe Institute of technology (KIT), Germany. Her research interests are in the area of swarm intelligence, evolutionary multi-objective optimisation and their applications in robotics, science and industry. She is an active member in several German and international societies such as IEEE and GI. She serves as an associate editor for IEEE Transactions on evolutionary computation and IEEE Transactions on cybernetics.
\end{IEEEbiography}
